The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-10-12 manuscript.Rmd
move section about US biodiversity first

Several factors may contribute to species being included in the regional lists but not having records in biodiversity databases. The first category of biases is linked to the likelihood of having specimens for these species in museum collections. For instance, rare species may never have been collected or may have only been collected a few times, and the corresponding records have not been digitized yet. Species that are difficult to preserve because they are large, very small, or fragile, are deposited in museums less frequently. The other category of biases is associated with data quality for these records. Some of these species may be in the databases but do not have geographic coordinates associated with them, and therefore would not be included in the results of our query. While it is difficult to assess biases associated with the likelihood of preservation of a species, we investigated how missing geographic coordinates are affecting the discrepancies between the checklists and the databases.

Two factors most likely contribute to explanations of why some species are in databases but are not included in the regional the checklists: (1) the species have been documented for the first time since the publication of the checklist, and (2) the species records were not accessible or known to the authors.

@@

>>>>

@@

Several factors may contribute to species being included in the regional lists but not having records in biodiversity databases. The first category of biases is linked to the likelihood having specimens for these species in digitized museum collections. Rare species may only have been collected a few times, and the corresponding records have not been digitized yet. Species that are difficult to preserve because they are large, very small, or fragile, are deposited in museums less frequently. The other category of biases is associated with data quality for these records. Some of these species may be in the databases but do not have geographic coordinates associated with them, and therefore would not be included in the results of our query. While it is difficult to assess biases associated with the likelihood of preservation of a species, we investigated how missing geographic coordinates are affecting the discrepancies between the checklists and the databases.

Two factors most likely contribute to explanations of why some species are in databases but are not included in the regional checklists: (1) the species have been documented for the first time since the publication of the checklist, and (2) the species records were not accessible or known to the authors.
